Mechanisation of Session-based Lambda Calculus Type Systems

### 2014-11-27 proposal/proposal.tex
Added effecting lambda abs. and Caires & Pfenning &/+ rules.

\usepackage{listings}
\usepackage{lstcoq}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{cmll}

\usepackage[style=alphabetic,sorting=nymt,natbib=true,
  maxbibnames=100]{biblatex}

@@

\input{macros}

@@

... lambda abstraction ...

@@

... here are the rules ...

Note that branch and choice both have some notion of branching (R rules for
+/L rules for \&) and at least for \& this is counter-intuitive in
session-based setting, since the intutition for \& is that of offering a
choice between alternatives rather than making the choice. Here, however, the
intuition should be extended to account for its location in the typing
judgement. The channel is on the left of the sequent which caires and pfenning
suggest as some service providing to the process.

@@

I shall review and update the above plan throughtout the project as I proceed
to the various milestones I have set out, and whenever I identify changing
circumstances.

>>>>

\usepackage{listings}
\usepackage{lstcoq}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{cmll}
\usepackage{prooftree}
\usepackage{amsmath}
\newcommand{\typestate}[2]{{#1}\gg{#2}}
\usepackage[style=alphabetic,sorting=nymt,natbib=true,
  maxbibnames=100]{biblatex}

@@

\input{propmacros}

@@

%% \begin{prooftree}
%% \AxiomC{$\Gamma , x \colon A \triangleright t \colon T \triangleleft \Gamma ' , x \colon B$}
%% \UnaryInfC{$\Gamma \triangleright t \colon (A \gg B) \rightarrow T \triangleleft \Gamma '$} 
%% \end{prooftree}

\begin{gather*}
  \frac{
    \typeds{\Gamma,\typedid{x}{A}}{t}{T}{\Gamma',\typedid{x}{B}}
  }{
    \typeds{\Gamma}{\abs{x}{t}}{\fn{\typestate{A}{B}}{T}}{\Gamma'}
  }\quad
\end{gather*}

@@

\input{sill-branch-choice-rules}

Note that branch and choice both have some notion of branching (R rules for
$\oplus$/L rules for $\with$) and at least for \& this is counter-intuitive in
a session-based setting, since the intutition for \& is that of
\emph{offering} a choice between alternatives rather than \emph{making} the
choice. Here, however, the intuition should be extended to account for its
location in the typing judgement. The channel is on the left of the sequent,
and \citeauthor{Caires:2010:STI} suggest one consider the context as services
being provided to the typed process. Thus, the type of channels in the context
is really the type of the other endpoint of the channel, and the typed process
behaves according to the dual protocol. For example, considering $\SILLbranchLTwo$, and taking $A^\bot$ to represent the dual of a protocol $A$, the typed process is behaving according to the protocol $\BChoice{A^\bot}{B^\bot}$, selecting from alternatives (in this case, $\inrterm$) and then behaving according to the selected protocol (in this case, protocol $B^\bot$).

@@

There is a risk of being unable to perform the side-effecting extension as
sketched in \S \ref{sec:approach}. I shall review and update the above plan
throughtout the project as I proceed to the various milestones I have set out,
and if required will alter the above plans if necessary.
